Approximation as Differentiation notes

### 2025-03-03 notes/sec/grothendieck.tex
Think this is a bit better.

\begin{definition}[Grothendieck construction for $F$]
Suppose a functor $F: D \to \Cat$. The \emph{Grothendieck construction} $\Grothendieck{D}F$ for $F$ is the
category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an object $X$ of $F(I)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ paired with a morphism $F(f)(X)
\to Y$ in $F(J)$.
\end{itemize}
\end{definition}

\noindent When $F$ is contravariant, a morphism from $(I, X)$ to $(J, Y)$ is a morphism $f: I \to J$ in $D$
paired with a morphism $X \to F(f)(Y)$ in $F(I)$.

@@

In $\Fam(C)$ we then have that:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and an indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[\idxf{X}, \idxf{Y}])$ in $\Fam(C)$ where $[\idxf{X},
\idxf{Y}]$ denotes the indexed family which maps every $f: X \to Y$ in $\Fam(C)$ to
$\prod_{I}\reindex{Y}{\idxf{f}}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any morphism $f: X \times Y \to Z$
to $g: X \to [Y, Z]$ with:
\begin{itemize}
\item $\idxf{g}(i) = (j \mapsto \idxf{f}(i, j): J \to K, j \mapsto \famf{f}_{i,j} \comp \inj_{Y_j}: Y \to
\reindex{Z}{j \mapsto \idxf{f}(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $\famf{g}(i) = \lambda_{\prod_{J}}(j \mapsto \famf{f}_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i
\to X_i \biprod Y_j$ for every $j \in J$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idxf{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\famf{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{I}\reindex{Y}{f} \biprod X_i \to Y_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:

>>>>

\begin{definition}[Grothendieck construction for $F$]
Suppose a functor $F: D \to \Cat$. The \emph{Grothendieck construction} $\Grothendieck{D}F$ for $F$ is the
category where:
\begin{itemize}
\item objects $X$ are pairs of an object $\idx{X}$ of $D$ and an object $\faml{X}$ of $F(\idx{X})$;
\item morphisms $f: X \to Y$ are morphisms $\idx{f}: \idx{X} \to \idx{Y}$ in $D$ paired with morphisms
$\faml{f}: F(f)(\faml{X}) \to \faml{Y}$ in $F(\idx{Y})$.
\end{itemize}
\end{definition}

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ is a morphism $\idx{f}: \idx{X} \to \idx{J}$ in
$D$ paired with morphisms $\faml{f}: \faml{X} \to F(f)(\faml{Y})$ in $F(\idx{X})$.

@@

\noindent In $\Fam(C)$ the objects $X$ are thus pairs of a set $\idx{X}$ and indexed family $\faml{X}$ in
$\Fam(\idx{X},C)$ and morphisms $f: X \to Y$ are functions $\idx{f}: \idx{X} \to \idx{Y}$ paired with a
morphism $\faml{f}: X \to \reindex{Y}{f}$ in $\Fam(\idx{X},C)$.

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[\idx{X}, \idx{Y}])$ in $\Fam(C)$ where $[\idx{X},
\idx{Y}]$ denotes the indexed family which maps every $f: X \to Y$ in $\Fam(C)$ to
$\prod_{I}\reindex{Y}{\idx{f}}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any morphism $f: X \times Y \to Z$
to $g: X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{g}(i) = (j \mapsto \idx{f}(i, j): J \to K, j \mapsto \faml{f}_{i,j} \comp \inj_{Y_j}: Y \to
\reindex{Z}{j \mapsto \idx{f}(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $\faml{g}(i) = \lambda_{\prod_{J}}(j \mapsto \faml{f}_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i
\to X_i \biprod Y_j$ for every $j \in J$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\faml{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{I}\reindex{Y}{f} \biprod X_i \to Y_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:
